### 2011-12-13 paper.tex
Added stuff for the paper (style sheets, sample code. Feel free to run pdflatex -shell-escape paper.tex to see a beautiful minted *.pdf produced before your very eyes)

%IMPORTANT: BECAUSE WE ARE USING MINTED, YOU MUST SAY pdflatex -shell-escape paper.tex

\documentclass[11pt, letterpaper, oneside] {article}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{fullpage}
\usepackage{minted}

\begin{document}
\parindent = 0cm

Testing minted.
\begin{minted}{c}
int main() {
  printf("hello, world");
  return 0;
}
\end{minted}
\end{document}

### 2011-12-13 uistSample.tex
Added stuff for the paper (style sheets, sample code. Feel free to run pdflatex -shell-escape paper.tex to see a beautiful minted *.pdf produced before your very eyes)

\documentclass{article}

\usepackage{times}
\usepackage{uist}

\begin{document}

% --- Copyright notice ---
\conferenceinfo{UIST'11}{October 16-19, 2011, Santa Barbara, CA, USA}
\CopyrightYear{2011}
\crdata{978-1-4503-0716-1/11/10}

% Uncomment the following line to hide the copyright notice
% \toappear{}
% ------------------------

\bibliographystyle{plain}

\title{Standard UIST Conference Format:\\
       Preparing Camera-Ready Submissions}

%%
%% Note on formatting authors at different institutions, as shown below:
%% Change width arg (currently 7cm) to parbox commands as needed to
%% accommodate widest lines, taking care not to overflow the 17.8cm line width.
%% Add or delete parboxes for additional authors at different institutions. 
%% If additional authors won't fit in one row, you can add a "\\"  at the
%% end of a parbox's closing "}" to have the next parbox start a new row.
%% Be sure NOT to put any blank lines between parbox commands!
%%

\author{
\parbox[t]{9cm}{\centering
	     {\em Author One}\\
	     User Interface Laboratory\\
             ABC Corporation\\
	     1234 Anywhere Road\\
	     Anytown, NY 10027 USA\\
	     +1-212-555-1212\\
	     one@abc.com}
\parbox[t]{9cm}{\centering
	     {\em Author Two}\\
	     Universit\'{e} de XYZ\\
	     5678 rue des Parapluies\\
	     99099 Cr\`{e}me de Menthe, FRANCE\\
	     +33-12-34-56-78\\
	     deux@uvw.xyz.fr}
}

\maketitle

\abstract
Each paper should begin with an abstract, followed by a set of keywords, both
placed in the left column of the first page under the left half of the title.
All body text, such as this paragraph, should be set in 10 point Times Roman
type, with 11 points between successive baselines.  (We will repeat that later
in this document to make sure that you do not forget.)

\classification{H5.2 [Information interfaces and presentation]:
User Interfaces. - Graphical user interfaces.}

\terms{Design, Human Factors (Your general terms must be any of the
  following 16 designated terms: Algorithms, Management, Measurement,
  Documentation, Performance, Design, Economics, Reliability,
  Experimentation, Security, Human Factors, Standardization,
  Languages, Theory, Legal Aspects, Verification. See ~\cite{ACMTerms} for more details.)}

\keywords{Guides, instructions, formatting.}

\tolerance=400 
  % makes some lines with lots of white space, but 	
  % tends to prevent words from sticking out in the margin

\section{INTRODUCTION}
The {\em UIST} proceedings represent the final archival records of
the conference.  We would like the proceedings to have a
uniform, high quality appearance.  To accomplish this, authors must follow
the format specified here.

In essence, we ask that whatever text formatting program you use,
you format your paper exactly like this document.  Please
match the type style, type size, line spacing, indentation, and layout
format as closely as you can.  In fact, if you received this document online
as a LaTeX file, along with its accompanying uist.sty style file, you can
use it as a template.

Use an A4 or 8.5"$\times$11" sheet of paper. Center the image on the page.
The whole image of your text must {\em completely} fit in a 17.8 cm$\times$23.5 cm box. 
If you are not using LaTeX with the uist.sty style
file, then the recommendations we have included here should help you match this
sample with the facilities you do have, such as Microsoft Word.

\section{TITLE AND AUTHORS}
\textbf{The authors list should be removed for blind review.}

The title, author's names and affiliations run across the full width of the
page.  We also recommend phone number and e-mail address, if available.  (See
the top of this page for an example of two names with different addresses.
If only one address is needed, center all text on the page.)

Here are the typographic details:
\begin{itemize}
\item Title area: 1 column, 5.9 cm (2 1/3") length, 17.8 cm (7") width.
\item Title: 18 point Helvetica Bold---mixed cases
\item Names: 12 point Times Italic
\item Addresses, Telephone, E-mail:  12 point Times Roman
\end{itemize}

\section{FIRST PAGE COPYRIGHT NOTICE}
Remember to leave 2.54 cm of blank space at the bottom of the left
column of the first  page,  as on this page. You must leave this space for
the copyright notice on {\em all} submissions intended for publication in the
proceedings.

Please note that the first author of all accepted submissions
will have to sign a copyright release form.  Those forms will be sent with the
acceptance letters and need to be returned rapidly.  We encourage the contact 
persons of each submission to keep track of their co-authors' locations because 
they will be responsible for rapidly collecting the signatures.

\section{TWO COLUMNS}
All body text should be in 10 point Times Roman, with 11 points between
successive baselines.

After the title use a double-column format as shown here. Column width is 8.5
cm, with 0.8 cm between columns (for a total image width still equal to 17.8
cm).  Total text length should remain between 23.2 and 24 cm (9 1/4") .
Right margins should be justified, not ragged.   Separate each paragraph by a
blank line (and do not indent them)  Hyphenation is at your own discretion.
If at all possible, the two columns of the last page should be of equal length.
(The  LaTeX uist.sty file does not do this automatically, so
you will need to insert the commands \verb+\linebreak+ and \verb+\newpage+
at an appropriate point on the last page to justify the current line and
force a new column.)

\section{SECTIONS}
The title of a section should be in 9 point Helvetica Bold font in all
capitals. Notice that the sections, subsections, and subsubsections are not
numbered in this document, but you may number them if you want.

\subsection{Subsections}
The title of a subsection should be in 9 point Helvetica Bold with only the
initial letters of each word capitalized. (Note: Words like ``the'' and ``a''
are not capitalized unless they start a title.)

\subsubsection{Subsubsections.} The heading for a subsubsection should be in
9 point Helvetica Oblique (italic) with initial letters
capitalized. (Note: Words like ``the'' and ``a'' are not capitalized
unless they start a title.)  The subsubsection heading should {\em not}
appear on its own separate line.

\section{TYPESETTING}
Please use the fonts specified in this description
so that we can produce a conference proceedings that looks like a unified
document, rather than a collection of unrelated papers thrown
together.  The body of your paper should use 10 point Times Roman type,
set with an 11 point vertical spacing between baselines (also known as
1 point of leading).
Do not use a sans-serif font (e.g., Helvetica),  except for emphasis, headings
and the title, as described above.
Computer Modern Roman or another font with serifs should be used {\em only} 
as a last resort if Times Roman is not available. 
Macintosh users should use the font named Times.

\section{FIGURES}
Figures should be inserted at the appropriate point in your text, or
optionally floated to the top or bottom of the page, as was done with
Figure \ref{fig-example}.  If necessary, figures can extend up to the
width of the full two columns: 17.8 cm (7") if necessary.

The quality of your images and figures is critical. Your paper, if accepted, will
be printed in the high quality print proceedings, and will also be available 
for download on the ACM Digital Library where readers may read it online
and zoom in to see the details.

Screen dumps should be captured at the screen resolution and
use a lossless format such as TIFF.
Photos should have a resolution of at least 150dpi, and preferably
300dpi or 600dpi. They may be slightly compressed, e.g. in JPEG,
if this does not degrade quality (use the "Better" or "8/10" setting).
Diagrams, data plots and schemas should use a vector format
rather than a raster format where possible.

\begin{figure}[tb]
\vspace{1.9in}
\caption{A figure caption.  It is set in 9 point Helvetica type, with a
0.5 cm wider margin on both left and right sides.} 
\label{fig-example}
\end{figure}

Remember also that some readers may never see anything other than a 
oor photocopy of your paper, so make sure that the figure will still be 
readable (try to see how it looks after recopying it a couple of times).

\section{PRODUCING PDF FILES}
Submissions as well as final versions of your paper must be submitted in PDF format.
Most typesetting systems can produce PDF either directly or by using
a virtual printer. If you cannot produce PDF directly, you can produce
a PostScript file and then use a PostScript to PDF converter. Either way,
make sure that your PDF file is correct by viewing it with a standard
PDF reader such as Adobe's Acrobat.

\section{REFERENCES AND CITATIONS}
Your references should appear in the standard CACM format: a numbered list at
the end of the paper, ordered alphabetically by first author, and referenced by
number in brackets as shown here~\cite{badenov91,henry-etal92,zaranka81}.
(See the examples of citations at the end of this document, and the other
examples on p. 12 of the April 94 issue of the {\em Communications of the
ACM.}) 
References should be materials accessible to the public:
books, articles in standard journals, and papers in open conference
proceedings. 
Internal technical reports should be avoided unless easily accessible (i.e. you
can give the address to obtain it).  Personal communications should be
acknowledged, not referenced. Be sure to remove all dangling references and citations.

\section{LANGUAGE, STYLE AND CONTENT}
The written and spoken language of UIST is English. Spelling and punctuation may use
 any dialect of English (e.g., British, Canadian, US, etc.) provided this is done 
consistently. Hyphenation is optional. To ensure suitability for an international audience, 
please pay attention to the following:
\begin{itemize}
\item Try to avoid long or complex sentence structures. 
\item Briefly define or explain all technical terms that may be unfamiliar to readers.
\item Explain all acronyms the first time they are used in your text – e.g., 
“Digital Signal Processing (DSP)”.
\item Explain local references (e.g., not everyone knows all city names in a particular country).
\item Explain “insider” comments. Ensure that your whole audience understands any
reference whose meaning you do not describe (e.g., do not assume that everyone has 
used a Macintosh or a particular application).
\item Explain colloquial language and puns. Understanding phrases like “red herring” 
may require a local knowledge of English.  Humor and irony are difficult to translate.
\item Use unambiguous forms for culturally localized con-cepts, such as times, dates, 
currencies and numbers (e.g., “1-5- 97” or “5/1/97” may mean 5 January or 1 May, 
and “seven o’clock” may mean 7:00 am or 19:00).  For cur-rencies, indicate 
equivalences – e.g., “Participants were paid 10,000 lire, or roughly \$5.”
\item Be careful with the use of gender-specific pronouns ({\em he, she}) and other gendered 
words ({\em chairman, manpower, man-months}). Use inclusive language that is gender-
neutral (e.g., {\em she or he, they, s/he, chair, staff, staff-hours, person-years}). 
See~\cite{GenderNeutral} for further advice and ex-amples regarding gender and 
other personal attributes.
\item If possible, use the full (extended) alphabetic character set for names of persons, 
institutions, and places (e.g., Gr{\o}nb{\ae}k, Lafreni\'{e}re, S\^{a}nchez, Universit\"{a}t, 
Wei{\ss}enbach, Z\"{u}llighoven, {\AA}rhus, etc.).  These characters are already included in 
most versions of Times, Helvetica, and Arial fonts.
\end{itemize}

\section{HEADERS, FOOTERS AND PAGE NUMBERING}
Do not use headers, footers or footnotes. Page numbers, footers and headers will
be added when the Conference Proceedings are assembled. Papers submitted
to the paper chairs for review should have page numbers (to help the review process).

\section{OTHER CONSIDERATIONS}
\subsection{No Private Material}
Presentations should not contain any proprietary or confidential
material. Please clear all materials before submitting or presenting them.
Submission of pictures of identifiable people should be done only with the
understanding that responsibility for obtaining appropriate permissions rests
with the paper's authors.

\subsection{Equations}
Displayed equations should be centered, with optional equation numbers 
right-justified to the right margin of the column.

% use \newpage to break the columns on the last page so they have equal length
% if the break occurs in the middle of a paragraph, insert \linebreak before \newpage

\section{BLIND REVIEW}
For archival submissions, UIST requires a “blind review.” To prepare your 
submission for blind review, remove author and institutional identities in 
the title and header areas of the paper. You may also need to remove all 
of the Acknowledgments text. Authors should \textbf{not} use anonymous citations 
(by blanking their name or using Anonymous as an author) for references 
to their previous work. Instead, authors should 
refer  to previous work in 
the third person (i.e. as if they were not the authors). This will ensure that 
reviewers can take into 
\linebreak
\newpage
account previous research by the authors. 
Further suppression of identity in the body of the paper is left to the authors' discretion.
 For more details, 
see the submission guidelines and checklist for your submission category.

\section{CONCLUSION}
It is important that you write for the UIST audience.  Please read previous years’
{\em Proceedings} to understand the writing style and conventions that successful 
authors have used.  It is particularly important that you state clearly what you 
have done, not merely what you plan to do, and explain how your work is
different from previously published work, i.e., what is the unique contribution
that your work makes to the field?  Please consider what the reader will learn
from your submission, and how they will find your work useful.  If you write with
these questions in mind, your work is more likely to be successful, both in being
accepted into the Conference, and in influencing the work of our field.

\section{ACKNOWLEDGMENTS}
\begin{center}
\textbf{This section should be left blank for blind review}
\end{center}

The authors would like to acknowledge the contributions of many previous
editors in the writing and formatting of this document.  This document is based on
the {\em CHI '94} format-ting guidelines.

%%%	You can use bibtex if you like, but I've hardwired in these 
%%%	references to avoid sending you a separate .bib file.
\begin{thebibliography}{9}

\bibitem{ACMTerms} How to Classify Works Using ACM’s Computing
Classification System. {http://www.acm.org/class/how\_to\_use.html}.

\bibitem{badenov91}  Badenov, B. Effects of prolonged use of WIMP user
interfaces on Alces americana and Glaucomys volans.
In {\em Proceedings of UIST '87}
(February 30--April 1, Graceland, TN), ACM, NY, 1987, pp. 231--240.

\bibitem{henry-etal92} Henry, T.R., Yeatts, A.K., Hudson, S.E., Myers, B.A.,
and Feiner, S.K.  A nose gesture interface device: Extending virtual realities.
{\em Presence 1}, 2 (Spring 1992), 258--261.

\bibitem{GenderNeutral} Schwartz, M. Guidelines for Bias-Free Writing.
Indiana University Press, Bloomington, IN, USA, 1995.

\bibitem{zaranka81} Zaranka, W., Ed. {\em The Brand-X Anthology of Poetry:  A
Parody Anthology.}  Apple-wood Books, Cambridge, MA, 1981.
\end{thebibliography}

\end{document}

### 2011-12-13 test.py

@@ -2,5 +2,9 @@ import HaPy
 
 mod = HaPy.LoadHaskellModule("./Mod.o")
 print mod.one.toInt()
-print mod.plus(19, mod.one).toInt()
+
+for i in range(3):
+  for j in range(5):
+    print mod.plus(i, j).toInt()
+
 print mod.greeting.toString()

### 2011-12-13 HaPy.py
noted retrieveBool bug in TODO

@@ -5,7 +5,7 @@ haPy = cdll.LoadLibrary("./libhapy.so")
 
 # Set libhapy typeinfo
 haPy.retrieveInt.restype = c_int
-haPy.retrieveBool.restype = lambda i: False if i is 0 else True
+haPy.retrieveBool.restype = lambda i: False if i is 0 else True #TODO: not working, must debug
 haPy.retrieveDouble.restype = c_double
 haPy.retrieveString.restype = c_char_p
 

### 2011-12-13 HaPy.py
changed currying implementation on python side

@@ -10,55 +10,54 @@ haPy.retrieveDouble.restype = c_double
 haPy.retrieveString.restype = c_char_p
 
 class HaskellObject:
-	def __init__(self, objPtr):
-		self.ptr = objPtr
-	
-	def __call__(self, *args):
-		if args:
-			arg = args[0]
-			applyFun = None
-			if isinstance(arg, int):
-				applyFun = haPy.applyInt
-			elif isinstance(arg, float):
-				applyFun = haPy.applyDouble
-			elif isinstance(arg, bool):
-				applyFun = haPy.applyBool
-			elif isinstance(arg, str):
-				applyFun = haPy.applyString
-			elif isinstance(arg, HaskellObject):
-				applyFun = haPy.applyOpaque
-				arg = arg.ptr
-			return apply(HaskellObject(applyFun(self.ptr, arg)), args[1:])
-		else:
-			return self
+    def __init__(self, objPtr):
+        self.ptr = objPtr
+    
+    def __call__(self, arg, *args):
+        applyFun = None
+        if isinstance(arg, int):
+            applyFun = haPy.applyInt
+        elif isinstance(arg, float):
+            applyFun = haPy.applyDouble
+        elif isinstance(arg, bool):
+            applyFun = haPy.applyBool
+        elif isinstance(arg, str):
+            applyFun = haPy.applyString
+        elif isinstance(arg, HaskellObject):
+            applyFun = haPy.applyOpaque
+            arg = arg.ptr
+        else:
+            raise TypeError("Unknown Object Type!")
+        self.ptr = applyFun(self.ptr, arg)
+        return self(*args) if args else self
 
-	def toInt(self):
-		return haPy.retrieveInt(self.ptr)
-	
-	def toBool(self):
-		return haPy.retrieveBool(self.ptr)
+    def toInt(self):
+        return haPy.retrieveInt(self.ptr)
+    
+    def toBool(self):
+        return haPy.retrieveBool(self.ptr)
 
-	def toDouble(self):
-		return haPy.retrieveDouble(self.ptr)
+    def toDouble(self):
+        return haPy.retrieveDouble(self.ptr)
 
-	def toString(self):
-		return haPy.retrieveString(self.ptr)
+    def toString(self):
+        return haPy.retrieveString(self.ptr)
 
 
 class HaskellModule:
-	def __init__(self, modulePath):
-		self.path = modulePath
+    def __init__(self, modulePath):
+        self.path = modulePath
 
-	def __getattr__(self, name):
[…]

### 2011-12-13 test.py

@@ -3,8 +3,7 @@ import HaPy
 mod = HaPy.LoadHaskellModule("./Mod.o")
 print mod.one.toInt()
 
-for i in range(3):
-  for j in range(5):
-    print mod.plus(i, j).toInt()
+print mod.plus(1, "cows").toInt()
+
 
 print mod.greeting.toString()

### 2011-12-14 HaPy.py
At leaset nominal implementation of module lookup. Doesn't seem to quite work though

@@ -51,7 +51,7 @@ class HaskellModule:
 
 	def __getattr__(self, name):
 		symPtr = haPy.getSymbol(self.path, name)
-		if symPtr is None:
+		if symPtr is 0:
 			raise AttributeError
 
 		return HaskellObject(symPtr)

### 2011-12-14 test.py

@@ -1,10 +1,4 @@
 import HaPy
 
-mod = HaPy.LoadHaskellModule("./Mod.o")
-print mod.one.toInt()
-
-for i in range(3):
-  for j in range(5):
-    print mod.plus(i, j).toInt()
-
-print mod.greeting.toString()
+mod = HaPy.LoadHaskellModule("GHC.Paths")
+print mod.ghc

### 2011-12-14 paper.tex
Example Haskell code is getting ready; Newton's method works, just having trouble parsing the input string.

@@
-%IMPORTANT: BECAUSE WE ARE USING MINTED, YOU MUST SAY pdflatex -shell-escape paper.tex
+% IMPORTANT: BECAUSE WE ARE USING MINTED, YOU MUST SAY pdflatex -shell-escape paper.tex
 
@@
 
+\section{Motivation}
+It is a truth universally acknowledged, that a single Python module in possession of a good GUI, must be in want of a Haskell backend.
+Joking aside, three trends are clear when looking at the most recent State of Haskell survey and other data: in the first place, Haskellers primarily use Haskell for mathematical analysis, parsing/compiling, and (increasingly) web development; importantly, GUI development in Haskell is almost non-existent.
+Secondly, Python remains a popular language for creating GUIs, because of its high-level, human-readable syntax and intuitive ease of use.
+Lastly, Python code is much slower than the corresponding C code, while Haskell's performance is generally almost as good as C's for most use cases.
+This is in spite of the fact that Python and Haskell are both very high-level languages.
+
+\section{Further work}
+In future, HaPy could support dynamic conversion from GADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type.
+\section{Refernces}
+System.Plugins stuff.
+
 Testing minted.
-\begin{minted}{c}
-int main() {
-  printf("hello, world");
-  return 0;
-}
+\begin{minted}{haskell}
+fib :: [Int]
+fib = 1 : 1 : foldWith (+) fib (tail fib)
 \end{minted}

### 2011-12-14 example.hs

@@ -1,0 +1,30 @@
+import Data.List
+import Data.List.Split
+
+-- we represent polynomials as lists of pairs of (Double, Double)
+-- the pair (a, n) corresponds to the term a*x^n
+type Polynomial = [(Double, Double)]
+
+parsePolynomial :: String -> Polynomial
+parsePolynomial = map convertTerm . parse
+    where parse str = parseAcc "" [] str
+          parseAcc acc terms (c:cs) = case c of
+                                        '+' -> parseAcc "" (acc:terms) cs
+                                        '-' -> parseAcc "-" (acc:terms) cs
+                                        _   -> parseAcc (acc ++ [c]) terms cs
+          convertTerm = (\term -> ((read $ head $ splitOn "x^" term) :: Double, (read $ last $ splitOn "x^" term) :: Double))
+
+evaluate :: Polynomial -> Double -> Double
+evaluate poly x = foldl (\acc (coeff, exp) -> acc + coeff * (x ** exp)) 0 poly
+
+polyDerivative :: Polynomial -> Polynomial
+polyDerivative = map (\(coeff, exp) -> (coeff * exp, exp - 1))
+
+newton :: (Fractional t, Ord t) => (t -> t) -> (t -> t) -> t -> [t]
+newton f f' x0 = iterate next x0
+    where next xn = xn - ((f xn)/(f' xn))
+
+findZero :: (Fractional t, Ord t) => (t -> t) -> (t -> t) -> t -> t -> t
+findZero f f' x0 epsilon = case find (\x -> (abs $ f x) < epsilon) (newton f f' x0) of
+                             Just root -> root
+                             Nothing   -> undefined

### 2011-12-15 HaPy.py
now with typechecking! (note: typechecking still not fully tested with haskell objects, etc)

@@ -1,63 +1,168 @@
 from ctypes import *
+import os.path
+import subprocess
 
 # Load libhapy
-haPy = cdll.LoadLibrary("./libhapy.so")
+hapy = cdll.LoadLibrary("./libhapy.so")
 
 # Set libhapy typeinfo
-haPy.retrieveInt.restype = c_int
-haPy.retrieveBool.restype = lambda i: False if i is 0 else True #TODO: not working, must debug
-haPy.retrieveDouble.restype = c_double
-haPy.retrieveString.restype = c_char_p
+hapy.retrieveInt.restype = c_int
+hapy.retrieveBool.restype = lambda i: False if i is 0 else True #TODO: not working, must debug
+hapy.retrieveDouble.restype = c_double
+hapy.retrieveString.restype = c_char_p
+
+class HaskellType:
+    def __init__(self, name, cls, applyFun, retrieveFun):
+        self.name = name
+        self.cls = cls
+        self.applyFun = applyFun
+        self.retrieveFun = retrieveFun
+
+    def __repr__(self):
+        return self.__class__.__name__ + "(" + self.name + ")"
+
+_types = [ HaskellType("Int"    , int   , hapy.applyInt    , hapy.retrieveInt)
+         , HaskellType("Bool"   , bool  , hapy.applyBool   , hapy.retrieveBool)
+         , HaskellType("Double" , float , hapy.applyDouble , hapy.retrieveDouble)
+         , HaskellType("String" , str   , hapy.applyString , hapy.retrieveString)
+         ]
+_KNOWN_TYPES = { type.name:type for type in _types }
+
+def _isGeneric(type):
+    return type[0].islower()
+
+def _knownTypeFromClass(cls):
+    for type in _KNOWN_TYPES.values():
+        if type.cls == cls:
+            return type
+    return None
+                
+class HaskellFunctionType:
+    def __init__(self, name, argTypes, returnType):
+        self.name = name
+        self.argTypes = argTypes
+        self.returnType = returnType
+
+    def __repr__(self):
+        return self.__class__.__name__ + "(" + repr(self.name) + ", " + repr(self.argTypes) + ", " + repr(self.returnType) + ")"
+
+    @staticmethod
+    def parse(s):
+        [name, rest] = s.split("::")
+        name = name.strip()
+        types = rest.split("->")
+        types = map(str.strip, types)
+        return HaskellFunctionType(name, types[:-1], types[-1])
+
 
 class HaskellObject:
[…]

### 2011-12-15 Mod.hs

@@ -2,14 +2,14 @@ module Mod where
 import Data.HashTable
 import Data.Int
 
-one :: Integer
+one :: Int
 one = 1
 
 plus :: Int -> Int -> Int
 plus = (+)
 
-hash :: String -> Int32
-hash = hashString
+hash :: String -> Int
+hash = fromIntegral.hashString
 
 greeting :: String
 greeting = "hi there, from Haskell!"

### 2011-12-15 test.py

@@ -1,9 +1,8 @@
 import HaPy
 
 mod = HaPy.LoadHaskellModule("Mod")
-print mod.one.toInt()
+print mod.one
 
-print mod.plus(1, mod.one).toInt()
+print mod.plus(1, 2)
 
-
-print mod.greeting.toString()
+print mod.greeting

### 2011-12-15 HaPy.py
Now works with haskell objects

@@ -105,6 +105,10 @@ class HaskellObject:
             if arg.isFullyApplied() and arg.returnType == nextType:
                 self.ptr = hapy.applyOpaque(self.ptr, arg.ptr) # TODO: currently, both pointers are freed. instead of always freeing pointers, use finalizers
                 arg.ptr = None
+                del self.argTypes[0]
+            else:
+                raise TypeError("Expected haskell object of type " + nextType
+                                + "but received type " + arg.returnType)
         else:
             raise TypeError("Cannot handle " + arg.__class__.__name__)
 

### 2011-12-15 Mod.hs

@@ -13,3 +13,8 @@ hash = fromIntegral.hashString
 
 greeting :: String
 greeting = "hi there, from Haskell!"
+
+haskellObject = [1::Int,2,3,4,5]
+
+mySum :: [Int] -> Int
+mySum = sum

### 2011-12-15 test.py

@@ -6,3 +6,7 @@ print mod.one
 print mod.plus(1, 2)
 
 print mod.greeting
+
+haskellObject = mod.haskellObject
+print haskellObject
+print mod.mySum(haskellObject)

### 2011-12-15 HaPy.py
start of python import hooks

@@ -1,3 +1,4 @@
+import sys
 from ctypes import *
 
 # Load libhapy
@@ -9,9 +10,28 @@ haPy.retrieveBool.restype = lambda i: False if i is 0 else True #TODO: not worki
 haPy.retrieveDouble.restype = c_double
 haPy.retrieveString.restype = c_char_p
 
+# Define finder and loader
+class HaPyImporter:
+    def find_module(self, fullname, path=None):
+        print "Find module called"
+        return None        
+
+    def load_module(self, fullname):
+        return None
+
+def useHaskellImporter(pathItem):
+    if pathItem is haskellPathItem:
+        return HaPyImporter()
+    else:
+        raise ImporterError
+
+haskellPathItem = "<<Haskell>>"
+__path__ = [haskellPathItem]
+sys.path_hooks.append(useHaskellImporter)
+
 class HaskellObject:
     def __init__(self, objPtr):
-        self.ptr = objPtr
+        self._ptr = objPtr
     
     def __call__(self, arg, *args):
         applyFun = None
@@ -25,23 +45,23 @@ class HaskellObject:
             applyFun = haPy.applyString
         elif isinstance(arg, HaskellObject):
             applyFun = haPy.applyOpaque
-            arg = arg.ptr
+            arg = arg._ptr
         else:
             raise TypeError("Unknown Object Type!")
-        self.ptr = applyFun(self.ptr, arg)
+        self._ptr = applyFun(self._ptr, arg)
         return self(*args) if args else self
 
     def toInt(self):
-        return haPy.retrieveInt(self.ptr)
+        return haPy.retrieveInt(self._ptr)
     
     def toBool(self):
-        return haPy.retrieveBool(self.ptr)
+        return haPy.retrieveBool(self._ptr)
 
     def toDouble(self):
-        return haPy.retrieveDouble(self.ptr)
+        return haPy.retrieveDouble(self._ptr)
 
     def toString(self):
-        return haPy.retrieveString(self.ptr)
+        return haPy.retrieveString(self._ptr)
 
 
 class HaskellModule:
@@ -55,7 +75,7 @@ class HaskellModule:
 
         return HaskellObject(symPtr)
 
-def LoadHaskellModule(moduleName):
+def loadHaskellModule(moduleName):
     ''' moduleName should be of the standard "Data.Int"
         format using in Haskell import statements
         So we need to search the package.conf?

### 2011-12-15 HaPy.py
added option to disable typechecking of Haskell objects

@@ -68,7 +68,9 @@ class HaskellObject:
     def isFullyApplied(self):
         return self.argTypes == []
 
-    def __call__(self, arg, *args):
+    def __call__(self, arg, *args, **kwargs):
+        typecheck = kwargs.get("typecheck", False)
+
         # make sure object is still valid
         if self.ptr is None:
             raise RuntimeError("Value already retrieved: object no longer callable")
@@ -102,7 +104,7 @@ class HaskellObject:
                 raise TypeError("Expected argument of type " + nextTypeInfo.cls.__name__
                                 + " but received type " + arg.__class__.__name__ + ".")
         elif isinstance(arg, HaskellObject):
-            if arg.isFullyApplied() and arg.returnType == nextType:
+            if not typecheck or (arg.isFullyApplied() and arg.returnType == nextType):
                 self.ptr = hapy.applyOpaque(self.ptr, arg.ptr) # TODO: currently, both pointers are freed. instead of always freeing pointers, use finalizers
                 arg.ptr = None
                 del self.argTypes[0]

### 2011-12-15 HaPy.hs
now using the python import mechanism

@@ -30,6 +30,7 @@ getSymbol modName_c symName_c = do
     status <- Plug.load objectFilePath [] [] symName
     case status of
         Plug.LoadFailure msg -> do -- Symbol not found, return error
+            print msg
             return $ castPtrToStablePtr nullPtr 
         Plug.LoadSuccess _ sym -> do -- Return symbol
             sPtr <- newStablePtr sym

### 2011-12-15 HaPy.py

@@ -8,7 +8,7 @@ hapy = cdll.LoadLibrary("./libhapy.so")
 
 # Set libhapy typeinfo
 hapy.retrieveInt.restype = c_int
-hapy.retrieveBool.restype = lambda i: False if i is 0 else True #TODO: not working, must debug
+hapy.retrieveBool.restype = lambda i: False if i == 0 else True #TODO: not working, must debug
 hapy.retrieveDouble.restype = c_double
 hapy.retrieveString.restype = c_char_p
 
@@ -55,25 +55,26 @@ class HaskellFunctionType:
         types = map(str.strip, types)
         return HaskellFunctionType(name, types[:-1], types[-1])
 
-
-# Define finder and loader
+# Define importer for haskell modules as part of the python import mechanism
 class HaPyImporter:
     def find_module(self, fullname, path=None):
-        print "Find module called"
-        return None        
+        if (fullname.split('.'))[0] == "HaPy":
+            return self
+        else:
+            raise ImportError
 
     def load_module(self, fullname):
-        return None
+        modName = '.'.join((fullname.split('.'))[1:])
+        mod = loadHaskellModule(modName)
+        mod.__file__ = "<HaskellModule>"
+        mod.__loader__ = self
+        sys.modules.setdefault(fullname, mod)
+        return mod
 
-def useHaskellImporter(pathItem):
-    if pathItem is haskellPathItem:
-        return HaPyImporter()
-    else:
-        raise ImporterError
-
-haskellPathItem = "<<Haskell>>"
-__path__ = [haskellPathItem]
-sys.path_hooks.append(useHaskellImporter)
+# After much experimentation it has been found that the combination
+# of __path__ and adding the importer to the meta_path works.
+__path__ = []
+sys.meta_path.append(HaPyImporter())
 
 class HaskellObject:
     def __init__(self, objPtr, name, argTypes, returnType):

### 2011-12-15 test.py

@@ -1,12 +1,3 @@
-import HaPy
+from HaPy import Mod
 
-mod = HaPy.LoadHaskellModule("Mod")
-print mod.one
-
-print mod.plus(1, 2)
-
-print mod.greeting
-
-haskellObject = mod.haskellObject
-print haskellObject
-print mod.mySum(haskellObject)
+print Mod.plus(4,5)

### 2011-12-15 HaPy.py
Removed dead code

@@ -36,23 +36,6 @@ def _knownTypeFromClass(cls):
         if type.cls == cls:
             return type
     return None
-                
-class HaskellFunctionType:
-    def __init__(self, name, argTypes, returnType):
-        self.name = name
-        self.argTypes = argTypes
-        self.returnType = returnType
-
-    def __repr__(self):
-        return self.__class__.__name__ + "(" + repr(self.name) + ", " + repr(self.argTypes) + ", " + repr(self.returnType) + ")"
-
-    @staticmethod
-    def parse(s):
-        [name, rest] = s.split("::")
-        name = name.strip()
-        types = rest.split("->")
-        types = map(str.strip, types)
-        return HaskellFunctionType(name, types[:-1], types[-1])
 
 
 class HaskellObject:

### 2011-12-15 HaPy.hs
load local modules from subdirs

@@ -10,6 +10,7 @@ import GHC
 import Module
 import GHC.Paths (libdir)
 import System.FilePath
+import Data.List.Split
 
 -- Placeholder type used where the actual type is hidden or unknown
 data Opaque 
@@ -38,9 +39,10 @@ getSymbol modName_c symName_c = do
 
 objectFileForModuleName :: String -> IO String
 objectFileForModuleName modName = do
-    -- Search for the module first in current directory
+    -- Search for the module first in current directory and sub dirs
+    let modulePath = foldr (</>) "" (splitOn "." modName)
     dot <- getCurrentDirectory
-    let localPath = dot </> modName ++ ".o"
+    let localPath = dot </> (modulePath ++ ".o")
     isLocal <- doesFileExist localPath
     if isLocal then
         return localPath

### 2011-12-15 HaPy.py

@@ -1,7 +1,7 @@
-import sys
 from ctypes import *
-import os.path
+import sys
 import subprocess
+import os
 
 # Load libhapy
 hapy = cdll.LoadLibrary("./libhapy.so")
@@ -150,12 +150,12 @@ class HaskellObject:
 
 class HaskellModule:
     def __init__(self, name, dirs):
-        self.path = os.path.join(dirs[0], name) #TODO: support multiple directories (the load command in haskell already does this: we just need to pass the string list through)
-        self.interface = _getInterface(self.path)
+        self.name = name 
+        self.interface = _getInterface(self.name)
 
     def __getattr__(self, name):
         if name in self.interface:
-            symPtr = hapy.getSymbol(self.path, name)
+            symPtr = hapy.getSymbol(self.name, name)
             if symPtr is not None:
                 return HaskellObject(symPtr, *self.interface[name])._retrieve()
             else:
@@ -163,8 +163,9 @@ class HaskellModule:
         else:
             raise AttributeError("Function not found")
 
-def _getInterface(file):
-    interfaceOutput = subprocess.check_output(["ghc", file, "-e", ":browse"])
+def _getInterface(modName):
+    filePath = os.path.join(os.getcwd(), os.sep.join(modName.split('.'))) + ".o"
+    interfaceOutput = subprocess.check_output(["ghc", filePath, "-e", ":browse"])
     functions = interfaceOutput.splitlines()
     functions = map(_parseInterfaceLine, functions)
     return {func[0]: func for func in functions}

### 2011-12-15 test.py

@@ -1,3 +1,5 @@
-from HaPy import Mod
+import HaPy
 
-print Mod.plus(4,5)
+mod = HaPy.loadHaskellModule("Mod")
+
+print mod.plus(4,5)

### 2011-12-15 HaPy.hs
changed haskell object lifetime management

@@ -75,7 +75,6 @@ hostPackage mName = runGhc (Just libdir) $ do
 applyArg :: StablePtr (a -> Opaque) -> a -> IO (StablePtr Opaque)
 applyArg sPtr arg = do
     fun <- deRefStablePtr sPtr
-    _ <- freeStablePtr sPtr
     res <- return (fun arg)
     newStablePtr res
 
@@ -107,7 +106,6 @@ foreign export ccall applyOpaque :: StablePtr (Opaque -> Opaque) ->
                                       StablePtr Opaque -> IO (StablePtr Opaque)
 applyOpaque funPtr argPtr = do
     arg <- deRefStablePtr argPtr
-    _ <- freeStablePtr argPtr
     applyArg funPtr arg
 
 
@@ -116,8 +114,14 @@ applyOpaque funPtr argPtr = do
 retrieveResult :: StablePtr a -> IO(a)
 retrieveResult sPtr = do
     res <- deRefStablePtr sPtr
-    _ <- freeStablePtr sPtr
     return res
+
+
+-- free pointer
+foreign export ccall freePtr :: StablePtr a -> IO ()
+freePtr sPtr = do
+    _ <- freeStablePtr sPtr
+    return ()
 
 -- export for each supported type
 

### 2011-12-15 HaPy.py

@@ -1,6 +1,7 @@
 from ctypes import *
 import os.path
 import subprocess
+import weakref
 
 # Load libhapy
 hapy = cdll.LoadLibrary("./libhapy.so")
@@ -44,24 +45,26 @@ class HaskellObject:
         self.name = name
         self.argTypes = argTypes
         self.returnType = returnType
+        self._finalizer = weakref.ref(self, lambda wr, ptr=self.ptr: hapy.freePtr(ptr))
 
     def __repr__(self):
         return self.__class__.__name__ + "(" + repr(self.name) + ", " + repr(self.argTypes) + ", " + repr(self.returnType) + ")"
 
     def isFullyApplied(self):
-        return self.argTypes == []
+        return not self.argTypes
 
-    def __call__(self, arg, *args, **kwargs):
+    def __call__(self, *allArgs, **kwargs):
         typecheck = kwargs.get("typecheck", False)
 
-        # make sure object is still valid
-        if self.ptr is None:
-            raise RuntimeError("Value already retrieved: object no longer callable")
+        if not allArgs:
+            return self._retrieve()
 
+        arg = allArgs[0]
+        args = allArgs[1:]
         if self.isFullyApplied():
             return RuntimeError("Too many arguments")
 
-        # adjust generic type if it exists
+        # adjust generic type if it exists TODO: fix
         if _isGeneric(self.argTypes[0]):
             nextTypeInfo = _knownTypeFromClass(arg.__class__)
             oldType = self.argTypes[0]
@@ -71,26 +74,26 @@ class HaskellObject:
                 newType = arg.returnType
             else:
                 raise TypeError("Cannot handle " + arg.__class__.__name__)
-            self.argTypes = [newType if t == oldType else t for t in self.argTypes]
+            argTypes = [newType if t == oldType else t for t in self.argTypes]
             if self.returnType == oldType:
-                self.returnType = newType
+                returnType = newType
+        else:
+            argTypes = self.argTypes
+            returnType = self.returnType
 
         # apply argument as appropriate
-        nextType = self.argTypes[0]
+        nextType = argTypes[0]
         if nextType in _KNOWN_TYPES:
             nextTypeInfo = _KNOWN_TYPES[nextType]
             if isinstance(arg, nextTypeInfo.cls):
-                self.ptr = nextTypeInfo.applyFun(self.ptr, arg)
-                del self.argTypes[0]
+                return HaskellObject(nextTypeInfo.applyFun(self.ptr, arg), self.name, argTypes[1:], returnType)(*args)
[…]

### 2011-12-15 test.py

@@ -4,9 +4,17 @@ mod = HaPy.LoadHaskellModule("Mod")
 print mod.one
 
 print mod.plus(1, 2)
+# plusOne = mod.plus(1)
+# print plusOne(2)
+# print plusOne(3)
 
 print mod.greeting
 
 haskellObject = mod.haskellObject
 print haskellObject
 print mod.mySum(haskellObject)
+
+# print mod.myId(4)
+print mod.myId("cheesecake")
+# print mod.myId(True)
+# print mod.myId(False)

### 2011-12-15 HaPy.py
latest on loading local sub dirs

@@ -164,8 +164,13 @@ class HaskellModule:
             raise AttributeError("Function not found")
 
 def _getInterface(modName):
-    filePath = os.path.join(os.getcwd(), os.sep.join(modName.split('.'))) + ".o"
-    interfaceOutput = subprocess.check_output(["ghc", filePath, "-e", ":browse"])
+    paths = modName.split('.')
+    mod = paths[-1]
+    olddir = os.getcwd()
+    path = os.path.join(os.getcwd(), os.sep.join(paths[:-1]))
+    os.chdir(path)
+    interfaceOutput = subprocess.check_output(["ghc", mod, "-e", ":browse"])
+    os.chdir(olddir)
     functions = interfaceOutput.splitlines()
     functions = map(_parseInterfaceLine, functions)
     return {func[0]: func for func in functions}

### 2011-12-15 test.py

@@ -1,5 +1,5 @@
 import HaPy
 
-mod = HaPy.loadHaskellModule("Mod")
+Mod = HaPy.loadHaskellModule("Sub.Mod")
 
-print mod.plus(4,5)
+print Mod.plus(4,5)

### 2011-12-15 HaPy.py
Importing sub modules mostly works

@@ -151,9 +151,13 @@ class HaskellObject:
 class HaskellModule:
     def __init__(self, name, dirs):
         self.name = name 
-        self.interface = _getInterface(self.name)
+        self.interface = None
+        self.__str__ = name
+        self.__path__ = []
 
     def __getattr__(self, name):
+        if not self.interface:
+            self.interface = _getInterface(self.name)
         if name in self.interface:
             symPtr = hapy.getSymbol(self.name, name)
             if symPtr is not None:

### 2011-12-15 test.py

@@ -1,5 +1,3 @@
-import HaPy
-
-Mod = HaPy.loadHaskellModule("Sub.Mod")
+from HaPy.Sub import Mod
 
 print Mod.plus(4,5)

### 2011-12-15 test.py
fixed mismatch in test following merge

@@ -1,17 +1,17 @@
 from HaPy.Sub import Mod
 
-print mod.plus(1, 2)
-# plusOne = mod.plus(1)
+print Mod.plus(1, 2)
+# plusOne = Mod.plus(1)
 # print plusOne(2)
 # print plusOne(3)
 
-print mod.greeting
+print Mod.greeting
 
-haskellObject = mod.haskellObject
+haskellObject = Mod.haskellObject
 print haskellObject
-print mod.mySum(haskellObject)
+print Mod.mySum(haskellObject)
 
-# print mod.myId(4)
-print mod.myId("cheesecake")
-# print mod.myId(True)
-# print mod.myId(False)
+# print Mod.myId(4)
+print Mod.myId("cheesecake")
+# print Mod.myId(True)
+# print Mod.myId(False)

### 2011-12-15 HaPy.hs
added getIfaceFilePath to the haskell to aid in loading type info

@@ -37,17 +37,33 @@ getSymbol modName_c symName_c = do
             sPtr <- newStablePtr sym
             return $ castToOpaquePtr sPtr
 
+foreign export ccall getInterfaceFilePath :: CString -> IO (CString)
+getInterfaceFilePath modName_c = do
+    modName <- peekCString modName_c
+    objFile <- localModuleFilePath modName
+    let hiFile = replaceExtension objFile ".hi"
+    isLocal <- doesFileExist hiFile
+    if isLocal then
+        newCString hiFile
+    else 
+        newCString ""
+
 objectFileForModuleName :: String -> IO String
 objectFileForModuleName modName = do
     -- Search for the module first in current directory and sub dirs
-    let modulePath = foldr (</>) "" (splitOn "." modName)
-    dot <- getCurrentDirectory
-    let localPath = dot </> (modulePath ++ ".o")
+    localPath <- localModuleFilePath modName
     isLocal <- doesFileExist localPath
     if isLocal then
         return localPath
     else do -- Else look in for a cabal installed package (I'm aware that this is a hack)
         externalModuleObjectFilePath modName
+
+localModuleFilePath :: String -> IO String
+localModuleFilePath modName = do
+    let modulePath = foldr (</>) "" (splitOn "." modName)
+    dot <- getCurrentDirectory
+    let localPath = dot </> (modulePath ++ ".o")
+    return localPath
 
 externalModuleObjectFilePath :: String -> IO String
 externalModuleObjectFilePath mod = do

### 2011-12-15 HaPy.py

@@ -12,6 +12,7 @@ hapy.retrieveInt.restype = c_int
 hapy.retrieveBool.restype = lambda i: False if i == 0 else True #TODO: not working, must debug
 hapy.retrieveDouble.restype = c_double
 hapy.retrieveString.restype = c_char_p
+hapy.getInterfaceFilePath.restype = c_char_p
 
 class HaskellType:
     def __init__(self, name, cls, applyFun, retrieveFun):
@@ -154,10 +155,10 @@ class HaskellModule:
             raise AttributeError("Function not found")
 
 def _getInterface(modName):
-    paths = modName.split('.')
-    mod = paths[-1]
+    ifaceFilePath = hapy.getInterfaceFilePath(modName)
     olddir = os.getcwd()
-    path = os.path.join(os.getcwd(), os.sep.join(paths[:-1]))
+    path = os.path.dirname(ifaceFilePath)
+    mod = os.path.splitext(os.path.basename(ifaceFilePath))[0]
     os.chdir(path)
     interfaceOutput = subprocess.check_output(["ghc", mod, "-e", ":browse"])
     os.chdir(olddir)

### 2011-12-15 test.py

@@ -1,17 +1,3 @@
-from HaPy.Sub import Mod
-
-print Mod.plus(1, 2)
-# plusOne = Mod.plus(1)
-# print plusOne(2)
-# print plusOne(3)
-
-print Mod.greeting
-
-haskellObject = Mod.haskellObject
-print haskellObject
-print Mod.mySum(haskellObject)
-
-# print Mod.myId(4)
-print Mod.myId("cheesecake")
-# print Mod.myId(True)
-# print Mod.myId(False)
+import HaPy
+mod = HaPy.loadHaskellModule("GHC.Paths")
+print mod.libdir

### 2011-12-15 HaPy.hs
added doesModuleExist to exported Haskell API

@@ -37,6 +37,15 @@ getSymbol modName_c symName_c = do
             sPtr <- newStablePtr sym
             return $ castToOpaquePtr sPtr
 
+foreign export ccall doesModuleExist :: CString -> IO (Bool)
+doesModuleExist modName_c = do
+    modName <- peekCString modName_c
+    local <- localModuleFilePath modName
+    external <- externalModuleObjectFilePath modName
+    isLocal <- doesFileExist local
+    isExternal <- doesFileExist external
+    return $ isLocal || isExternal
+
 foreign export ccall getInterfaceFilePath :: CString -> IO (CString)
 getInterfaceFilePath modName_c = do
     modName <- peekCString modName_c

### 2011-12-15 HaPy.py
typechecking fix for packages

@@ -155,13 +155,15 @@ class HaskellModule:
             raise AttributeError("Function not found")
 
 def _getInterface(modName):
-    ifaceFilePath = hapy.getInterfaceFilePath(modName)
-    olddir = os.getcwd()
-    path = os.path.dirname(ifaceFilePath)
-    mod = os.path.splitext(os.path.basename(ifaceFilePath))[0]
-    os.chdir(path)
-    interfaceOutput = subprocess.check_output(["ghc", mod, "-e", ":browse"])
-    os.chdir(olddir)
+    moduleLocation = hapy.getInterfaceFilePath(modName)[:-3]
+    try:
+        if (moduleLocation):
+            interfaceOutput = subprocess.check_output(["ghc", moduleLocation[:-3], "-e", ":browse"])
+        else:
+            interfaceOutput = subprocess.check_output(["ghc", "-e", ":browse " + modName])
+    except CalledProcessError:
+        return None
+
     functions = interfaceOutput.splitlines()
     functions = map(_parseInterfaceLine, functions)
     functions = filter(None, functions)

### 2011-12-15 test.py

@@ -1,3 +1,18 @@
 import HaPy
-mod = HaPy.loadHaskellModule("GHC.Paths")
-print mod.libdir
+mod = HaPy.loadHaskellModule("Sub.Mod")
+
+print mod.plus(1, 2)
+# plusOne = mod.plus(1)
+# print plusOne(2)
+# print plusOne(3)
+
+print mod.greeting
+
+haskellObject = mod.haskellObject
+print haskellObject
+print mod.mySum(haskellObject)
+
+# print mod.myId(4)
+print mod.myId("cheesecake")
+# print mod.myId(True)
+# print mod.myId(False)

### 2011-12-15 HaPy.hs
fixed testing if modules exist

@@ -11,6 +11,7 @@ import Module
 import GHC.Paths (libdir)
 import System.FilePath
 import Data.List.Split
+import qualified Control.Exception as Except
 
 -- Placeholder type used where the actual type is hidden or unknown
 data Opaque 
@@ -41,10 +42,14 @@ foreign export ccall doesModuleExist :: CString -> IO (Bool)
 doesModuleExist modName_c = do
     modName <- peekCString modName_c
     local <- localModuleFilePath modName
-    external <- externalModuleObjectFilePath modName
     isLocal <- doesFileExist local
-    isExternal <- doesFileExist external
-    return $ isLocal || isExternal
+    if isLocal then
+        return True
+    else
+        Except.catch
+            (seq (hostPackage modName) (return True))
+            (\e -> seq (e::Except.SomeException) (return False))
+    
 
 foreign export ccall getInterfaceFilePath :: CString -> IO (CString)
 getInterfaceFilePath modName_c = do

### 2011-12-15 HaPy.hs
importing now works properly!

@@ -47,7 +47,7 @@ doesModuleExist modName_c = do
         return True
     else
         Except.catch
-            (seq (hostPackage modName) (return True))
+            (hostPackage modName >> return True)
             (\e -> seq (e::Except.SomeException) (return False))
     
 

### 2011-12-15 HaPy.py

@@ -3,6 +3,7 @@ import sys
 import subprocess
 import weakref
 import os
+import imp
 
 # Load libhapy
 hapy = cdll.LoadLibrary("./libhapy.so")
@@ -50,11 +51,20 @@ class HaPyImporter:
 
     def load_module(self, fullname):
         modName = '.'.join((fullname.split('.'))[1:])
-        mod = loadHaskellModule(modName)
-        mod.__file__ = "<HaskellModule>"
+        if hapy.doesModuleExist(modName):
+            mod = loadHaskellModule(modName)
+            mod.__file__ = "<HaskellModule>"
+            mod.__path__ = None
+        else:
+            mod = HaPyImporter()
+            mod.__file__ = "<Stub>"
+            mod.__path__ = None
         mod.__loader__ = self
         sys.modules.setdefault(fullname, mod)
         return mod
+
+    def __getattr__(self, name):
+        raise AttributeError
 
 # After much experimentation it has been found that the combination
 # of __path__ and adding the importer to the meta_path works.
@@ -138,13 +148,13 @@ class HaskellObject:
 class HaskellModule:
     def __init__(self, name, dirs):
         self.name = name 
-        self.interface = None
+        self.interface = _getInterface(self.name)
         self.__str__ = name
         self.__path__ = []
 
     def __getattr__(self, name):
         if not self.interface:
-            self.interface = _getInterface(self.name)
+            raise AttributeError("Interface could not be loaded")
         if name in self.interface:
             symPtr = hapy.getSymbol(self.name, name)
             if symPtr is not None:
@@ -158,10 +168,13 @@ def _getInterface(modName):
     moduleLocation = hapy.getInterfaceFilePath(modName)[:-3]
     try:
         if (moduleLocation):
-            interfaceOutput = subprocess.check_output(["ghc", moduleLocation[:-3], "-e", ":browse"])
+            interfaceOutput = subprocess.check_output(["ghc", moduleLocation, "-e", ":browse"])
         else:
             interfaceOutput = subprocess.check_output(["ghc", "-e", ":browse " + modName])
-    except CalledProcessError:
+    except subprocess.CalledProcessError:
+        return None
+
+    if not interfaceOutput:
         return None
 
     functions = interfaceOutput.splitlines()

### 2011-12-15 test.py

@@ -1,18 +1,19 @@
-import HaPy
-mod = HaPy.loadHaskellModule("Sub.Mod")
+from HaPy.Sub import Mod
+print Mod.plus(1, 2)
 
-print mod.plus(1, 2)
-# plusOne = mod.plus(1)
+# import HaPy.Sub.Mod
+# print HaPy.Sub.Mod.plus(1, 2)
+# plusOne = Mod.plus(1)
 # print plusOne(2)
 # print plusOne(3)
 
-print mod.greeting
+# print Mod.greeting
 
-haskellObject = mod.haskellObject
-print haskellObject
-print mod.mySum(haskellObject)
+# haskellObject = Mod.haskellObject
+# print haskellObject
+# print Mod.mySum(haskellObject)
 
-# print mod.myId(4)
-print mod.myId("cheesecake")
-# print mod.myId(True)
-# print mod.myId(False)
+# # print Mod.myId(4)
+# print Mod.myId("cheesecake")
+# print Mod.myId(True)
+# print Mod.myId(False)

### 2011-12-15 Newton.hs
Began gui

@@ -1,3 +1,5 @@
+module Newton where
+
 import Data.List
 import Data.List.Split
 
@@ -20,6 +22,7 @@ evaluate poly x = foldl (\acc (coeff, exp) -> acc + coeff * (x ** exp)) 0 poly
 polyDerivative :: Polynomial -> Polynomial
 polyDerivative = map (\(coeff, exp) -> (coeff * exp, exp - 1))
 
+{-
 newton :: (Fractional t, Ord t) => (t -> t) -> (t -> t) -> t -> [t]
 newton f f' x0 = iterate next x0
     where next xn = xn - ((f xn)/(f' xn))
@@ -28,3 +31,4 @@ findZero :: (Fractional t, Ord t) => (t -> t) -> (t -> t) -> t -> t -> t
 findZero f f' x0 epsilon = case find (\x -> (abs $ f x) < epsilon) (newton f f' x0) of
                              Just root -> root
                              Nothing   -> undefined
+-}

### 2011-12-15 gui.py

@@ -1,0 +1,26 @@
+from Tkinter import *
+from HaPy import Newton
+
+class App:
+    def __init__(self, master):
+        frame = Frame(master)
+        frame.pack()
+
+        self.button = Button(frame, text="QUIT", fg="red", command=frame.quit)
+        self.button.pack(side=LEFT)
+
+        self.button = Button(frame, text="Evaluate", command=self.evaluate)
+        self.button.pack(side=LEFT)
+
+
+        self.inputBox = Text(frame)
+        self.inputBox.insert(END, "hi")
+        self.inputBox.pack(side=LEFT)
+
+    def evaluate(self):
+        poly = Newton.parsePolynomial("x + 1")
+        print Newton.evaluate(poly, 1.0)
+
+root = Tk()
+app = App(root)
+root.mainloop()

### 2011-12-15 HaPy.py
now reports errors in parsing and continues instead of dying

@@ -187,10 +187,14 @@ def _parseInterfaceLine(s):
         return None
     # TODO: parse class if present e.g. "Number a => a"
     if "=>" in s:
-        raise TypeError("typeclasses not yet supported")
+        # raise TypeError("typeclasses not yet supported")
+        print "typeclasses not yet supported, cannot parse: " + s
+        return None
     # TODO: parse functions properly
     if "(" in s:
-        raise TypeError("functions not yet supported")
+        # raise TypeError("functions not yet supported")
+        print "functions not yet supported, cannot parse: " + s
+        return None
     [name, rest] = s.split("::")
     name = name.strip()
     types = rest.split("->")

### 2011-12-15 HaPy.py
doubles now work properly

@@ -3,14 +3,13 @@ import sys
 import subprocess
 import weakref
 import os
-import imp
 
 # Load libhapy
 hapy = cdll.LoadLibrary("./libhapy.so")
 
 # Set libhapy typeinfo
 hapy.retrieveInt.restype = c_int
-hapy.retrieveBool.restype = lambda i: False if i == 0 else True #TODO: not working, must debug
+hapy.retrieveBool.restype = lambda i: False if i == 0 else True
 hapy.retrieveDouble.restype = c_double
 hapy.retrieveString.restype = c_char_p
 hapy.getInterfaceFilePath.restype = c_char_p
@@ -27,7 +26,8 @@ class HaskellType:
 
 _types = [ HaskellType("Int"    , int   , hapy.applyInt    , hapy.retrieveInt)
          , HaskellType("Bool"   , bool  , hapy.applyBool   , hapy.retrieveBool)
-         , HaskellType("Double" , float , hapy.applyDouble , hapy.retrieveDouble)
+         , HaskellType("Double" , float , lambda p, f: hapy.applyDouble(p, c_double(f)) , hapy.retrieveDouble)
+         # , HaskellType("Double" , float , hapy.applyDouble , hapy.retrieveDouble)
          , HaskellType("String" , str   , hapy.applyString , hapy.retrieveString)
          ]
 _KNOWN_TYPES = { type.name:type for type in _types }

### 2011-12-15 HaPy.hs
loading from external modules now

@@ -28,15 +28,36 @@ foreign export ccall getSymbol :: CString -> CString -> IO (StablePtr Opaque)
 getSymbol modName_c symName_c = do
     modName <- peekCString modName_c
     symName <- peekCString symName_c
-    objectFilePath <- objectFileForModuleName modName
-    status <- Plug.load objectFilePath [] [] symName
-    case status of
-        Plug.LoadFailure msg -> do -- Symbol not found, return error
-            print msg
+    result <- loadSym modName symName
+    case result of
+        Nothing -> do -- Symbol not found, return error
             return $ castPtrToStablePtr nullPtr 
-        Plug.LoadSuccess _ sym -> do -- Return symbol
+        Just sym -> do -- Return symbol
             sPtr <- newStablePtr sym
             return $ castToOpaquePtr sPtr
+
+loadSym :: String -> String -> IO (Maybe a)
+loadSym modName sym = do
+    isLocal <- isLocalMod modName
+    if isLocal then
+        localLoad modName sym
+    else
+        packageLoad modName sym
+
+localLoad :: String -> String -> IO (Maybe a)
+localLoad modName sym = do
+        objectFilePath <- localModuleFilePath modName
+        result <- Plug.load objectFilePath [] [] sym
+        case result of
+            Plug.LoadSuccess _ s -> return $ Just s
+            Plug.LoadFailure _ -> return Nothing
+
+packageLoad :: String -> String -> IO (Maybe a)
+packageLoad modName sym = do
+        objectFilePath <- externalModuleObjectFilePath modName
+        packageName <- hostPackage modName
+        Plug.initLinker
+        Plug.loadPackageFunction packageName modName sym
 
 foreign export ccall doesModuleExist :: CString -> IO (Bool)
 doesModuleExist modName_c = do
@@ -49,7 +70,11 @@ doesModuleExist modName_c = do
         Except.catch
             (hostPackage modName >> return True)
             (\e -> seq (e::Except.SomeException) (return False))
-    
+
+isLocalMod :: String -> IO (Bool)
+isLocalMod modName = do
+    local <- localModuleFilePath modName
+    doesFileExist local
 
 foreign export ccall getInterfaceFilePath :: CString -> IO (CString)
 getInterfaceFilePath modName_c = do
@@ -61,16 +86,6 @@ getInterfaceFilePath modName_c = do
         newCString hiFile
     else 
         newCString ""
-
-objectFileForModuleName :: String -> IO String
-objectFileForModuleName modName = do
[…]

### 2011-12-15 HaPy.py

@@ -188,12 +188,12 @@ def _parseInterfaceLine(s):
     # TODO: parse class if present e.g. "Number a => a"
     if "=>" in s:
         # raise TypeError("typeclasses not yet supported")
-        print "typeclasses not yet supported, cannot parse: " + s
+        #print "typeclasses not yet supported, cannot parse: " + s
         return None
     # TODO: parse functions properly
     if "(" in s:
         # raise TypeError("functions not yet supported")
-        print "functions not yet supported, cannot parse: " + s
+        #print "functions not yet supported, cannot parse: " + s
         return None
     [name, rest] = s.split("::")
     name = name.strip()

### 2011-12-15 test.py

@@ -1,5 +1,8 @@
-from HaPy.Sub import Mod
-print Mod.plus(1, 2)
+from HaPy.GHC import Paths
+from HaPy.System import FilePath
+
+libdir = Paths.libdir
+print libdir
 
 # import HaPy.Sub.Mod
 # print HaPy.Sub.Mod.plus(1, 2)

### 2011-12-15 gui.py
GUI is now functional

@@ -1,5 +1,7 @@
 from Tkinter import *
-from HaPy import Newton
+from HaPy import Calc
+
+LINEBEGIN = "lb"
 
 class App:
     def __init__(self, master):
@@ -12,14 +14,26 @@ class App:
         self.button = Button(frame, text="Evaluate", command=self.evaluate)
         self.button.pack(side=LEFT)
 
-
         self.inputBox = Text(frame)
-        self.inputBox.insert(END, "hi")
         self.inputBox.pack(side=LEFT)
+        self.inputBox.bind("<KeyPress>", self.onkeypress)
+        self.inputBox.mark_set(LINEBEGIN, INSERT)
+        self.inputBox.mark_gravity(LINEBEGIN, LEFT)
+
+        self.outputBox = Text(frame)
+        self.outputBox.pack(side=BOTTOM)
+
+    def onkeypress(self, e):
+        if e.keycode == 36:
+            self.evaluate()
 
     def evaluate(self):
-        poly = Newton.parsePolynomial("x + 1")
-        print Newton.evaluate(poly, 1.0)
+        expr = (self.inputBox.get(LINEBEGIN, INSERT)).strip()
+        self.inputBox.mark_set(LINEBEGIN, INSERT)
+        result = Calc.evaluate(expr)
+        self.outputBox.insert(END, result)
+        self.outputBox.insert(END, "\n")
+
 
 root = Tk()
 app = App(root)

### 2011-12-15 Calc.hs
worrying segfault

@@ -1,0 +1,69 @@
+{-# LANGUAGE OverloadedStrings #-}
+
+module Calc (evaluate) where
+import Data.ByteString (ByteString)
+import qualified Data.ByteString.Char8 as B8
+
+import Data.Attoparsec as P
+import Data.Attoparsec.Char8 (char8, endOfLine)
+import qualified Data.Attoparsec.ByteString.Char8 as P8
+
+import Control.Applicative hiding (many)
+import Data.Word (Word8)
+import Data.Char
+
+import Data.Maybe
+import Control.Monad
+
+data Expr = Add
+          | Subtract
+          | Multiply
+          | Divide
+          | Number Double
+          deriving Show
+
+operators = [("+", Add)
+            ,("-", Subtract)
+            ,("*", Multiply)
+            ,("/", Divide)
+            ]
+
+parseSpaces = skipMany P8.space
+
+parseNumber :: Parser Expr
+parseNumber = Number <$> P8.rational
+
+parseOperator :: Parser Expr
+parseOperator = (fromJust . (`lookup` operators)) <$> (choice $ map (string.fst) operators)
+
+-- pushNumber :: Parser ([Expr] -> [Expr])
+-- pushNumber = (:) <$> parseNumber
+
+-- pushOperator :: Parser ([Expr] -> [Expr])
+-- pushOperator = parseOperator <$> (head <$>
+--     where push op (e1:e2:exprs) = op e1 e2 : exprs
+-- pushOperator = push `liftM` parseOperator
+--     where push op (e1:e2:exprs) = op e1 e2 : exprs
+          -- push _ _ = fail "Stack too small"
+
+parseExpr :: Parser Expr
+parseExpr = parseSpaces *> choice [parseNumber, parseOperator] <* parseSpaces
+
+parseExprs :: Parser [Expr]
+parseExprs = many1 parseExpr
+
+evalExprs :: [Expr] -> Maybe [Double]
+evalExprs = foldl (flip changeStack) (Just [])
+    where changeStack (Number n) (Just stack)        = Just (n:stack)
+          changeStack Add        (Just (n1:n2:rest)) = Just (n2+n1:rest)
+          changeStack Subtract   (Just (n1:n2:rest)) = Just (n2-n1:rest)
+          changeStack Multiply   (Just (n1:n2:rest)) = Just (n2*n1:rest)
+          changeStack Divide     (Just (n1:n2:rest)) = Just (n2/n1:rest)
+          changeStack _          _                   = Nothing
+
[…]

### 2011-12-15 gui.py

@@ -29,8 +29,9 @@ class App:
 
     def evaluate(self):
         expr = (self.inputBox.get(LINEBEGIN, INSERT)).strip()
+        exprAscii = expr.encode("utf8", "ignore")
         self.inputBox.mark_set(LINEBEGIN, INSERT)
-        result = Calc.evaluate(expr)
+        result = Calc.evaluate(exprAscii)
         self.outputBox.insert(END, result)
         self.outputBox.insert(END, "\n")
 

### 2011-12-15 HaPy.py
added support for functions

@@ -33,7 +33,7 @@ _types = [ HaskellType("Int"    , int   , hapy.applyInt    , hapy.retrieveInt)
 _KNOWN_TYPES = { type.name:type for type in _types }
 
 def _isGeneric(type):
-    return type[0].islower()
+    return isinstance(type, str) and type[0].islower()
 
 def _knownTypeFromClass(cls):
     for type in _KNOWN_TYPES.values():
@@ -86,7 +86,7 @@ class HaskellObject:
         return not self.argTypes
 
     def __call__(self, *allArgs, **kwargs):
-        typecheck = kwargs.get("typecheck", False)
+        typecheck = kwargs.get("typecheck", True)
 
         if not allArgs:
             return self._retrieve()
@@ -124,11 +124,11 @@ class HaskellObject:
                 raise TypeError("Expected argument of type " + nextTypeInfo.cls.__name__
                                 + " but received type " + arg.__class__.__name__ + ".")
         elif isinstance(arg, HaskellObject):
-            if not typecheck or (arg.isFullyApplied() and arg.returnType == nextType):
+            if not typecheck or (arg.isFullyApplied() and arg.returnType == nextType) or tuple(arg.argTypes + [arg.returnType]) == nextType:
                 return HaskellObject(hapy.applyOpaque(self._ptr, arg._ptr), self.name, argTypes[1:], returnType)(*args)
             else:
-                raise TypeError("Expected haskell object of type " + nextType
-                                + "but received type " + arg.returnType)
+                raise TypeError("Expected haskell object of type " + str(nextType)
+                                + " but received type " + str(arg.returnType))
         else:
             raise TypeError("Cannot handle " + arg.__class__.__name__)
 
@@ -182,23 +182,42 @@ def _getInterface(modName):
     functions = filter(None, functions)
     return {func[0]: func for func in functions}
 
+
+
 def _parseInterfaceLine(s):
+    def avoidParenSplit(string, sep):
+        if "(" not in string:
+            return string.split(sep)
+
+        frontParts = string.split("(", 1)
+        backParts = frontParts[1].rsplit(")",1)
+        front = frontParts[0]
+        middle = "(" + backParts[0] + ")"
+        back = backParts[1]
+        return front.split(sep) + [middle] + back.split(sep)
+    def parsePossibleFunction(string):
+        if string[0] == "(" and string[-1] == ")":
+            string = string[1:-1]
+            types = avoidParenSplit(string, "->")
+            types = map(str.strip, types)
[…]

### 2011-12-17 paper.tex
outline of paper
expanded outline

@@
-% IMPORTANT: BECAUSE WE ARE USING MINTED, YOU MUST SAY pdflatex -shell-escape paper.tex
-
-\documentclass[11pt, letterpaper, oneside] {article}
-\usepackage{amsmath, amssymb, amsthm}
-\usepackage{fullpage}
+\documentclass[11pt, letterpaper, oneside, twocolumn] {article}
 \usepackage{minted}
@@
 \begin{document}
-\parindent = 0cm
+
+\title{HaPy \\
+Haskell for Python
+}
+\author{David Fisher, Ashwin Siripurapu, and William Rowan}
+\maketitle
+
+\section{Introduction}
 
@@
 
-\section{Further work}
+\section{Use}
+
+\subsection{Loading Haskell Modules}
+
+\subsection{Haskell types in Python}
+
+\section{Implementation}
+
+\subsection{Dynamic Loading of Haskell modules}
+
+\subsection{Function Currying}
+
+\subsection{Type checking}
+
+\section{Future work}
 In future, HaPy could support dynamic conversion from GADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type.
+
 \section{Refernces}
@@
 
-Testing minted.
-\begin{minted}{haskell}
-fib :: [Int]
-fib = 1 : 1 : foldWith (+) fib (tail fib)
-\end{minted}
 \end{document}

### 2011-12-17 paper.tex
outline

@@
 \section{Introduction}
+% - what is HaPy?
+% - focuses on ease of use
+%  - to acomplish this: should be pythonic
+%  - completely transparent!
+%  - no coding overhead on either side (shouldn't be aware that you're using haskell on python side, don't need to code for python in haskell -> should be able to use any haskell module on system)
 
@@
 This is in spite of the fact that Python and Haskell are both very high-level languages.
+% - general motivation: haskell and python are good at different things
+%  - in a large project: good to be able to do each piece in the best language
+%  - usefullness is inversely proportional to friction (so now maximally useful)
+% - example use case:
+%  - python GUI, haskell backend
+%  - (or existing python project)
+%  - (or existing haskell library)
 
@@
 \subsection{Loading Haskell Modules}
+% - super easy: all haskell modules represented as submodules of HaPy
+% - import HaPy.Data.List
 
 \subsection{Haskell types in Python}
+% - some automarshalled (haskell functions, haskell primitive types)
+% - others opaque
+% - support function currying
+%  - haskell functions in python have haskell-type access if desired
+%  - can be ignored
+%  - can apply a few arguments at once
+% -  returns a new function every time
+% - can apply opaque haskell types
+% - automatically marshall (if possible) once all args applied
 
@@
 \section{Future work}
-In future, HaPy could support dynamic conversion from GADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type.
+In future, HaPy could support dynamic conversion from ADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type.
 

### 2011-12-17 paper.tex
full outline

@@
 \section{Use}
+% - Meshing python and haskell semantics
 
@@
 % - super easy: all haskell modules represented as submodules of HaPy
+%  - standard haskell module represnetnation (e.x. System.Plugins) preserved
 % - import HaPy.Data.List
@@
 
+% - Split across three languages
+%  - to our surprise currently very little in C
+%  - choice of what language to work in for each feature
+% - Python side uses Ctypes to dynamically load our precompiled C and Haskell shared object file 
+%  - idea: in future statily compile C-python module
+
 \subsection{Dynamic Loading of Haskell modules}
+
+% - hs-plugins
 
@@
 
+% C interface supports applying one argument at a time for each of
+
 \subsection{Type checking}
 
+% David
+
 \section{Future work}
-In future, HaPy could support dynamic conversion from ADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type.
+
+\subsection{Type checking}
+
+% real type checking
+
+\subsection{Supporting more types}
+
+% marshalling lists
+% mashralling ADTs
+
+\subsection{Improved dynamic loading}
+
+% 64-bit bug
+% difficultly in loading preinstalled modules
+%  - plugins only supports very simply model (like assuming that .hi file is next to .o file)
+% requires dynamic libraries
+
+\subsection{Simplied install}
+
+% require user of compiled binary to have dynamically compiled binary of haskell libraries
+
+\subsection{Passing Python Callbacks}
 
 \section{Refernces}
-System.Plugins stuff.
+
+% hs-plugins 
+% missing py?
 

### 2011-12-17 paper.tex
section: dynamic loading of haskell modules

@@
 
-% - hs-plugins
+HaPy uses the HSPlugins package to dynamically load requested Haskell modules.
+HSPlugins supports more than just dynamic loading of external object files.
+Most of the meat of the package is in two crucial components: the loading of dependent modules and dynamic type checking.
+
+HaPy doesn't actually use the dynamic type checking features of HSPlugins.
+This feature requires that client Haskell supply static types to check against.
+This make sense for HSPlugins intended use case, the loading of plugins that implement known interfaces.
+We, however, need to be able to load any Haskell module with any interface at runtime.
+We therefore ask HSPlugins to load all symbols as an opaque data type (literally \emph{data Opaque}) which will loose its type information when passed back to the Python side anyway.
+
+HSPlugins supports a simple, but limited interface for loading modules.
+The client is expected to pass a string representing the path to the object file containing the requested module and a string representing the symbol to be loaded.
+An implicit expectation is that the Haskell interface file for the requested module sits next to the object file on the file system and has the same base name.
+
+While this condition holds for locally compiled modules (GHC by default generates the object file and interface file next to each other) this doesn't hold for Haskell packages installed on the system.
+Loading modules from these packages posed several challenges.
+The first is finding the location of a package's object file from the module name.
+The module \emph{System.Plugins}, for example, might be provided by the package \emph{plugins-1.5.1.4}.
+Fortunately, we are able to use the GHC api to do this lookup for us which we then translate into a path to the object file.
+
+Our method of doing so is not robust, however.
+Ideally, we would be able to ask GHC to invoke the same mechanism that it uses to lookup modules when the user requests packages in GHCi but the complexity and opacity of the GHC api made it impossible to do this in our timeframe.
+
+The second challenge involved satisfying HSPlugins assumption that the Haskell interface file sits next to the object file for the module.
+Packages might provide many different modules, the interface files for which are stored underneath the the package's base directory in a file structure mimicing the package structure.
+We had to thus copy the requested interface file to the location expected by HSPlugins.
+
+Again, this mechanism is not robust.
+It will be important to utilize GHC's import mechanism in the future.
+Properly importing both local and package modules will probably require either utilizing HSPlugins' low level api or abandoing it altogether.
 

### 2011-12-17 paper.tex
Wrote use section.

--- 2011-12-17 paper.tex
@@
 \documentclass[11pt, letterpaper, oneside, twocolumn] {article}
-\usepackage{minted}
+\usepackage{verbatim, minted}
 
@@
 \section{Introduction}
-% - what is HaPy?
-% - focuses on ease of use
-%  - to acomplish this: should be pythonic
-%  - completely transparent!
-%  - no coding overhead on either side (shouldn't be aware that you're using haskell on python side, don't need to code for python in haskell -> should be able to use any haskell module on system)
 
@@
 This is in spite of the fact that Python and Haskell are both very high-level languages.
-% - general motivation: haskell and python are good at different things
-%  - in a large project: good to be able to do each piece in the best language
-%  - usefullness is inversely proportional to friction (so now maximally useful)
-% - example use case:
-%  - python GUI, haskell backend
-%  - (or existing python project)
-%  - (or existing haskell library)
 
 \section{Use}
-
+Importing a Haskell module into a Python program is easy with HaPy: simply add the line
+\begin{minted}{python}
+from HaPy import HsModule
+\end{minted}
+to the head of any Python script. This will dynamically load the specified Haskell module, so that any Haskell function defined in HsModule can be accessed and executed by the Python script. \\
+Installing HaPy is similarly intuitive, but with the caveat that all libraries called by HaPy.hs must be dynamically-linkable.
+This means that all of the packages that HaPy.hs imports must be reinstalled with Cabal, using the \verb!--enable-shared!
+flag.
+\footnote{The requirement that these packages be dynamically-linkable is enforced by Python's ctypes module, which we use to marshall primitive types across the Haskell-Python interface.} \\
+However, Haskell packages that are used by the user's Haskell code need not be dynamically-linkable.
+Indeed, on the Haskell side, no special support is needed by the user; literally any standard Haskell code will run with HaPy.
+All the issues of marshalling data and passing data to and from the Foreign Function Interface are managed by the code in HaPy.hs \\
+This has the added benefit of enabling the user to call any code defined in the Haskell standard libraries from Python. 
 \subsection{Loading Haskell Modules}
-% - super easy: all haskell modules represented as submodules of HaPy
-% - import HaPy.Data.List
 
 \subsection{Haskell types in Python}
-% - some automarshalled (haskell functions, haskell primitive types)
-% - others opaque
-% - support function currying
-%  - haskell functions in python have haskell-type access if desired
-%  - can be ignored
-%  - can apply a few arguments at once
-% -  returns a new function every time
-% - can apply opaque haskell types
-% - automatically marshall (if possible) once all args applied
 
@@
 \section{Future work}
-In future, HaPy could support dynamic conversion from ADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type.
+In future, HaPy could support dynamic conversion from GADTs to Python types when instance of user-defined Haskell data are passed from the Haskell layer to the Python layer---in particular, Haskell's product types would map to Python classes while Haskell's sum types could be represented in Python by an enumerated type.
 

### 2011-12-17 paper.tex

--- 2011-12-17 paper.tex
@@
 \section{Use}
+Importing a Haskell module into a Python program is easy with HaPy: simply add the line
+\begin{minted}{python}
+from HaPy import HsModule
+\end{minted}
+to the head of any Python script. This will dynamically load the specified Haskell module, so that any Haskell function defined in HsModule can be accessed and executed by the Python script. \\
+Installing HaPy is similarly intuitive, but with the caveat that all libraries called by HaPy.hs must be dynamically-linkable.
+This means that all of the packages that HaPy.hs imports must be reinstalled with Cabal, using the \verb!--enable-shared!
+flag.
+\footnote{The requirement that these packages be dynamically-linkable is enforced by Python's ctypes module, which we use to marshall primitive types across the Haskell-Python interface.} \\
+However, Haskell packages that are used by the user's Haskell code need not be dynamically-linkable.
+Indeed, on the Haskell side, no special support is needed by the user; literally any standard Haskell code will run with HaPy.
+All the issues of marshalling data and passing data to and from the Foreign Function Interface are managed by the code in HaPy.hs \\
+This has the added benefit of enabling the user to call any code defined in the Haskell standard libraries from Python. 
 % - Meshing python and haskell semantics

### 2011-12-17 paper.tex
Added stuff about future work (converting ADTs to Python types) to paper

@@
 \section{Use}
-Importing a Haskell module into a Python program is easy with HaPy: simply add the line
+Our goal with HaPy is to allow the user to call arbitrary Haskell code while remaining committed to ``Pythonic'' syntax.
+In particular, importing a Haskell module into a Python program is easy with HaPy: simply add the line
 \begin{minted}{python}
@@
 \end{minted}
-to the head of any Python script. This will dynamically load the specified Haskell module, so that any Haskell function defined in HsModule can be accessed and executed by the Python script. \\
+or
+\beign{minted}{python}
+import HaPy.HsModule
+\end{minted}
+to the head of any Python script.
+This will dynamically load the specified Haskell module, so that any Haskell function defined in HsModule can be accessed and executed by the Python script, as though it were code defined in another Python module.
+For instance, if HsModule defines a function \verb!sum!
+which takes two real numbers and returns their sum, the result can be printed in Python with
+\begin{minted}{python}
+print HsModule.sum(first, second)
+\end{minted}
 Installing HaPy is similarly intuitive, but with the caveat that all libraries called by HaPy.hs must be dynamically-linkable.
@@
 \subsection{Loading Haskell Modules}
+As noted previously, the syntax for loading Haskell modules is identical to the normal Python import syntax.
+All Haskell modules are represented as submodules of the HaPy module, in order that the Python interpreter should not mistake them for Python modules.
+\\
+Furthermore, the Haskell module hierarchy is preserved, so for instance one can say
+\begin{minted}{python}
+import HaPy.Data.List
+\end{minted}
 % - super easy: all haskell modules represented as submodules of HaPy
@@
 \subsection{Supporting more types}
-
+In addition to marshalling primitive types across the Haskell-Python interface, we would eventually like to be able to marshall Python lists into Haskell lists and vice versa.
+One potential challenge here would be the marshalling of infinitely long, lazily-evaluated lists from Haskell to Python.
+\\
+A bigger challenge would be dynamically converting from algebraic data types (ADTs) defined in Haskell to Python objects; for example, a simple product type composed of Haskell primitives could be represented as a named tuple\footnote{Effectively a fixed-size dictionary} in Python.
 % marshalling lists

### 2011-12-17 paper.tex
Added section on passing Python callbacks.

@@
 \subsection{Passing Python Callbacks}
-
+Lastly, we would like to allow users to pass Python functions to Haskell; an example use case might be passing a comparison function for Haskell to use in sorting a list.
+Python's ctypes module already supports passing Python functions to C code (provided that the functions take only arguments which can be converted to C types), so presumably we would use this to facilitate the passing of Python function pointers to Haskell.
+Once we have a pointer to a Python function in C, Haskell data can be marshalled into an appropriate ctype for the function to act on, and the return type of the function can subsequently be converted back into a Haskell type.
 \section{Refernces}

### 2011-12-17 paper.tex
Final changes to the paper made.

@@
 \documentclass[11pt, letterpaper, oneside, twocolumn] {article}
-\usepackage{verbatim, minted}
+\usepackage{verbatim, minted, hyperref}
 
@@
 \section{Introduction}
+HaPy is an implementation of a foreign function interface from Python to Haskell with a strong focus on ease of use.
+In particular, HaPy entirely eliminates the need for FFI-related boilerplate code in either language.
+That is, Haskell modules can be used from Python without any modification.
+Moreover, from the programmer's perspective, imported Haskell functions are indistinguishable from native Python functions and Haskell modules are imported using the standard Python import syntax.
 % - what is HaPy?
 % - focuses on ease of use
-%  - to acomplish this: should be pythonic
+%  - to accomplish this: should be pythonic
 %  - completely transparent!
@@
 \section{Motivation}
-It is a truth universally acknowledged, that a single Python module in possession of a good GUI, must be in want of a Haskell backend.
-Joking aside, three trends are clear when looking at the most recent State of Haskell survey and other data: in the first place, Haskellers primarily use Haskell for mathematical analysis, parsing/compiling, and (increasingly) web development; importantly, GUI development in Haskell is almost non-existent.
-Secondly, Python remains a popular language for creating GUIs, because of its high-level, human-readable syntax and intuitive ease of use.
-Lastly, Python code is much slower than the corresponding C code, while Haskell's performance is generally almost as good as C's for most use cases.
-This is in spite of the fact that Python and Haskell are both very high-level languages.
+% It is a truth universally acknowledged, that a single Python module in possession of a good GUI, must be in want of a Haskell backend.
+Each programming language has its own unique set of strengths and weaknesses.
+Therefore, choice of language is important when starting a project.
+In a perfect world, we would be able to mix and match languages at will, using the perfect language for each part of a project.
+Unfortunately, interfacing different languages often causes significant overhead, more than eliminating the gains reaped from the language specialization.
+The authors have found that, in general, the usefulness of a foreign function interface is directly proportional to its ease of use.
+Therefore, we hope to entirely remove the overhead of calling Haskell from Python.
+\\
+Three trends are clear when looking at the most recent State of Haskell survey\cite{state_of_haskell} and other data: in the first place, Haskellers primarily use Haskell for mathematical analysis, parsing/compiling, and (increasingly) web development.
+Importantly, GUI development in Haskell is almost non-existent.
+Secondly, Python is a popular language for creating GUIs due to the existence of a variety of easy to use toolkits.
+Lastly, Haskell is much faster than Python.
+This suggests an example use-case: an application with a Python GUI and a Haskell backend.
 % - general motivation: haskell and python are good at different things
@@
 or
-\beign{minted}{python}
+\begin{minted}{python}
 import HaPy.HsModule
@@
 \end{minted}
-Installing HaPy is similarly intuitive, but with the caveat that all libraries called by HaPy.hs must be dynamically-linkable.
-This means that all of the packages that HaPy.hs imports must be reinstalled with Cabal, using the \verb!--enable-shared!
+Installing HaPy is similarly intuitive, but with the caveat that all libraries called by \verb!HaPy.hs!
+must be dynamically-linkable.
+This means that all of the packages that \verb!HaPy.hs!
+imports must be reinstalled with Cabal, using the \verb!--enable-shared!
 flag.
-\footnote{The requirement that these packages be dynamically-linkable is enforced by Python's ctypes module, which we use to marshall primitive types across the Haskell-Python interface.} \\
+\footnote{The requirement that these packages be dynamically-linkable stems from the fact that \texttt{ctypes} must be able to dynamically link to \texttt{HaPy.hs} (see \nameref{simple_install}) } \\
 However, Haskell packages that are used by the user's Haskell code need not be dynamically-linkable.
-Indeed, on the Haskell side, no special support is needed by the user; literally any standard Haskell code will run with HaPy.
-All the issues of marshalling data and passing data to and from the Foreign Function Interface are managed by the code in HaPy.hs \\
+Indeed, on the Haskell side, no special support is needed by the user; any standard Haskell code will run with HaPy (modulo the incompleteness of our type checker).
+All the issues of marshalling data and passing data to and from the Haskell foreign function interface are managed by the code in \verb!HaPy.hs!.
 This has the added benefit of enabling the user to call any code defined in the Haskell standard libraries from Python.
@@
 As noted previously, the syntax for loading Haskell modules is identical to the normal Python import syntax.
-All Haskell modules are represented as submodules of the HaPy module, in order that the Python interpreter should not mistake them for Python modules.
+All Haskell modules are represented as submodules of the HaPy module, so that the Python interpreter should not mistake them for Python modules.
 \\
@@
 
-\subsection{Haskell types in Python}
-% - some automarshalled (haskell functions, haskell primitive types)
-% - others opaque
-% - support function currying
-%  - haskell functions in python have haskell-type access if desired
-%  - can be ignored
-%  - can apply a few arguments at once
-% -  returns a new function every time
-% - can apply opaque haskell types
-% - automatically marshall (if possible) once all args applied
+\subsection{Haskell Types in Python}
+One of the main challenges in HaPy is the representation of Haskell data types in Python.
+Some primitive Haskell types (currently \verb!Bool!, \verb!Int!, \verb!Double!, and \verb!String!) are marshalled into the equivalent Python type.
+All other Haskell types are returned as opaque references: they can be passed to Haskell functions, but cannot be modified or inspected by other Python code.
+Use of Haskell functions is trivial: they can be called just like other Python functions.
+Arguments can be any of the supported primitive types, which will be marshalled, or Haskell object references, which are passed through.
+The return value will be automatically converted into a Python type if possible; otherwise, it will remain as an opaque Haskell reference.
+The Haskell functions do not behave exactly like other Python functions: they support currying.
+When they are called with too few arguments, a partially-applied function object is returned.
+This does not invalidate the original function - all functions and partially-applied functions can be called as many times as desired.
+We chose to do this because it naturally followed from the implementation (see \nameref{imp_currying}) and nicely mirrors the behavior of actual Haskell functions.
+Further, this functionality can be ignored if not desired.
+(The user only loses immediate too-few-argument errors.)
 
@@
 
-\subsection{Dynamic Loading of Haskell modules}
+\subsection{Dynamic Loading of Haskell Modules}
 
@@
 We, however, need to be able to load any Haskell module with any interface at runtime.
-We therefore ask HSPlugins to load all symbols as an opaque data type (literally \emph{data Opaque}) which will loose its type information when passed back to the Python side anyway.
+We therefore ask HSPlugins to load all symbols as an opaque data type (literally \verb!data Opaque!) which will loose its type information when passed back to the Python side anyway.
 
@@
 The first is finding the location of a package's object file from the module name.
-The module \emph{System.Plugins}, for example, might be provided by the package \emph{plugins-1.5.1.4}.
-Fortunately, we are able to use the GHC api to do this lookup for us which we then translate into a path to the object file.
+The module \verb!System.Plugins!, for example, might be provided by the package \verb!plugins-1.5.1.4!.
+Fortunately, we are able to use the GHC API to do this lookup for us which we then translate into a path to the object file.
 
 Our method of doing so is not robust, however.
-Ideally, we would be able to ask GHC to invoke the same mechanism that it uses to lookup modules when the user requests packages in GHCi but the complexity and opacity of the GHC api made it impossible to do this in our timeframe.
+Ideally, we would be able to ask GHC to invoke the same mechanism that it uses to lookup modules when the user requests packages in GHCi but the complexity and opacity of the GHC API made it impossible to do this in our timeframe.
 
 The second challenge involved satisfying HSPlugins assumption that the Haskell interface file sits next to the object file for the module.
-Packages might provide many different modules, the interface files for which are stored underneath the the package's base directory in a file structure mimicing the package structure.
+Packages might provide many different modules, the interface files for which are stored underneath the the package's base directory in a file structure mimicking the package structure.
 We had to thus copy the requested interface file to the location expected by HSPlugins.
@@
 It will be important to utilize GHC's import mechanism in the future.
-Properly importing both local and package modules will probably require either utilizing HSPlugins' low level api or abandoing it altogether.
+Properly importing both local and package modules will probably require either utilizing HSPlugins' low level API or abandoning it altogether.
 
 \subsection{Function Currying}
+\label{sec:imp_currying}
 
-% C interface supports applying one argument at a time for each of
+The Python-side wrapper around Haskell functions is implemented as a variable-argument callable Python object, which contains type information and an opaque pointer to the Haskell function.
+To evaluate an opaque Haskell function pointer from Python, it must be passed to a conversion function in Haskell (using the FFI) with its arguments, where it is re-cast as the appropriate type, applied, and returned to Python.
+Instead of many different conversion functions for different numbers of arguments, there is a single-argument conversion function for each argument type (one for each of the supported marshalled types and one for opaque types).
+Therefore, function calls to Haskell function objects are curried in Python, and arguments are pushed through the FFI one at a time.
+When there are no arguments left (as determined by the type checker), Python converts the opaque pointer to the known return type of the Haskell function.
 
-\subsection{Type checking}
+\subsection{Type Checking}
 
-% David
+As Haskell is statically typed, no runtime type checks occur when calling Haskell functions.
+If a dynamically loaded Haskell function is called with the wrong type, silent memory corruption occurs.
+This generally leads to a segfault, but can also lead to other sorts of nastiness (incorrect return values, etc).
+While this only occurs in the case of programmer error (i.e.
+passing incorrect arguments to a function), the result is not acceptable: a reasonable type error should be generated.
+Therefore, dynamic type checking is essential.
+There are two possible approaches to dynamic type checking.
+The first - and more preferable - approach is to use GHC's type checker.
+The advantage of this approach is clear: types will (almost tautologically) always be checked correctly, as - for our purposes - GHC is the canonical implementation of type checking.
+The second approach is to do anything else, which more or less boils down to writing your own type checker.
+Unfortunately, a full copy of GHC's type checker would be fairly difficult to write, so this leaves the type checker with some subset of types that it can properly check (the size of which is about logarithmically related to the work involved).
+We started with the first approach, but ran into major difficulties with the internal GHC API.
+It is largely undocumented and is complicated enough to make it very difficult to understand.
+On top of this, it appears fairly susceptible to change: we noticed some differences between GHC 7.0.3 (which we had installed) and GHC 7.2.2 (the latest release at this time).
+For these reasons, we decided to use the second approach.
+The current type checking system extracts the type information from Haskell files using GHCi's \verb!:browse!
+command.
+This provides information for both installed packages and local files.
+(While it does not require the Haskell source for installed packages, through some quirk it will not give type information for local files unless the source is present.
+However, we find this acceptable for the moment.)  Because we are calling GHCi externally, we receive this type information as a string.
+While we could have done this from any of our three project languages, we chose to keep track of the type information in Python.
+This lets the Python code know how to marshal specific data types before and after function calls and when it should request the final result of a function (i.e.
+when all the arguments have been applied) without adding additional signalling complexity to the FFI.
+Furthermore, Python can be fully in charge of displaying type errors.
+Currently, the type checker does not support a large class of different function types.
+Type classes are ignored.
+Any complex polymorphism does not work.
+Any data types that are fully specified in the type signature work.
 
-\section{Future work}
+\section{Future Work}
 
-\subsection{Type checking}
+While we have succeeded in making HaPy easy to use, HaPy is not nearly robust enough to use in a production application as of yet.
 
+\subsection{Type Checking}
+
+The current type checker is fragile for a couple reasons.
+First, it parses an output that is intended to be human readable and therefore lacks a formal specification and is subject to change.
+Second, most of the type checking is string-manipulation based, which is fragile.
+In the future, we would like to use GHC's type system.
+Although the API is difficult to understand, it is robust.
+Furthermore, there's no other way to get type checking completely right.
 % real type checking
 
-\subsection{Supporting more types}
-In addition to marshalling primitive types across the Haskell-Python interface, we would eventually like to be able to marshall Python lists into Haskell lists and vice versa.
-One potential challenge here would be the marshalling of infinitely long, lazily-evaluated lists from Haskell to Python.
-\\
-A bigger challenge would be dynamically converting from algebraic data types (ADTs) defined in Haskell to Python objects; for example, a simple product type composed of Haskell primitives could be represented as a named tuple\footnote{Effectively a fixed-size dictionary} in Python.
-% marshalling lists
-% mashralling ADTs
+\subsection{Supporting More Types}
+In addition to marshalling primitive types across the Haskell-Python interface, we would eventually like to be able to marshal Python lists into Haskell lists and vice versa.
+This would almost certainly be done through a C wrapper function for efficiency.
+One potential challenge here would be the marshalling of infinitely long, lazily-evaluated lists from Haskell to Python.\\
+Another challenge would be dynamically converting from algebraic data types (ADTs) defined in Haskell to Python objects; for example, a simple product type composed of Haskell primitives could be represented as a named tuple\footnote{Effectively a fixed-size dictionary} in Python, provided that it is created using record syntax.
+Surprisingly, non-record ADTs will be much harder to translate into Python types because the only way (to the authors' knowledge) of extracting their values is pattern matching.
 
-\subsection{Improved dynamic loading}
+\subsection{Improved Dynamic Loading}
+HaPy uses \verb!System.Plugins!
+to dynamically load Haskell modules, which assumes that the module's \verb!*.hi!
+file is located in the same directory as the corresponding \verb!*.o!
+file.
+As previously mentioned, this is not the case for packages.
+This forces us to do a kludgey workaround: we temporarily copy the \verb!*.hi!
+file into the same directory \verb!*.o!
+file before loading them.
+In the future, we would either like to move away from \verb!System.Plugins!
+or switch to its lower level API so we do not have this problem.
+% difficultly in loading preinstalled modules
+%  - plugins only supports very simply model (like assuming that .hi file is next to .o file)
+
+\subsection{Simplified Install}
+\label{sec:simple_install}
+While developing HaPy, we encountered a serious bug relating to dynamic linking. In 64-bit environments, this results segfaults when using the Haskell \verb!System.Plugins! library. \\
+Further, the Python \verb!ctypes!
+module dynamically links to our binary.
+Unfortunately, this requires that we build our binary with the \verb!-dynamic!
+flag, which causes GHC to link all of the libraries HaPy uses dynamically.
+This means that users of HaPy must use Cabal to reinstall several packages with the \verb!--enable-shared!
+option.
+We should be able to statically link all of our libraries, so that we can simply distribute a self-contained binary.
+Furthermore, we speculate that this might solve our 64-bit bug.
 
 % 64-bit bug
-% difficultly in loading preinstalled modules
-%  - plugins only supports very simply model (like assuming that .hi file is next to .o file)
+% require user of compiled binary to have dynamically compiled binary of haskell libraries
 % requires dynamic libraries
-
-\subsection{Simplied install}
-
-% require user of compiled binary to have dynamically compiled binary of haskell libraries
 
@@
 Lastly, we would like to allow users to pass Python functions to Haskell; an example use case might be passing a comparison function for Haskell to use in sorting a list.
-Python's ctypes module already supports passing Python functions to C code (provided that the functions take only arguments which can be converted to C types), so presumably we would use this to facilitate the passing of Python function pointers to Haskell.
-Once we have a pointer to a Python function in C, Haskell data can be marshalled into an appropriate ctype for the function to act on, and the return type of the function can subsequently be converted back into a Haskell type.
-\section{Refernces}
+Python's \verb!ctypes!
+module already supports passing Python functions to C code (provided that the functions take only arguments which can be converted to C types), so presumably we would use this to facilitate the passing of Python function pointers to Haskell.
+Once we have a pointer to a Python function in C, Haskell data can be marshalled into an appropriate \verb!ctype!
+for the function to act on, and the return type of the function can subsequently be converted back into a Haskell type.
 
+% references:
+% state of haskell survey
 % hs-plugins 
 % missing py?
+\begin{thebibliography}{99}
+\bibitem{haskell_plugins}
+  Stewart, Don,
+  \emph{Haskell Plugins}.
+  \url{http://hackage.haskell.org/package/plugins}
+\bibitem{state_of_haskell}
+  Tibell, Johan,
+  \emph{State of Haskell Survey, 2011}.
+  \url{http://blog.johantibell.com/2011/08/results-from-state-of-haskell-2011.html}
+\end{thebibliography}
 

### 2011-12-17 paper.tex
Some last-minute updates to the paper (got namerefs working)

@@
 flag.
-\footnote{The requirement that these packages be dynamically-linkable stems from the fact that \texttt{ctypes} must be able to dynamically link to \texttt{HaPy.hs} (see \nameref{simple_install}) } \\
+\footnote{The requirement that these packages be dynamically-linkable stems from the fact that \texttt{ctypes} must be able to dynamically link to \texttt{HaPy.hs} (see \nameref{sec:simple_install}) } \\
 However, Haskell packages that are used by the user's Haskell code need not be dynamically-linkable.
@@
 This does not invalidate the original function - all functions and partially-applied functions can be called as many times as desired.
-We chose to do this because it naturally followed from the implementation (see \nameref{imp_currying}) and nicely mirrors the behavior of actual Haskell functions.
+We chose to do this because it naturally followed from the implementation (see \nameref{sec:imp_currying}) and nicely mirrors the behavior of actual Haskell functions.
 Further, this functionality can be ignored if not desired.
@@
 
-\subsection{Function Currying}
-\label{sec:imp_currying}
+\subsection{Function Currying}\label{sec:imp_currying}
 
@@
 
-\subsection{Simplified Install}
-\label{sec:simple_install}
+\subsection{Simplified Install}\label{sec:simple_install}
 While developing HaPy, we encountered a serious bug relating to dynamic linking. In 64-bit environments, this results segfaults when using the Haskell \verb!System.Plugins! library. \\
